Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-14 implementation/implementation.tex
New figures

\begin{table}[t!]
    \centering
    \begin{tabular}{|c c c|}
        \hline
        Parameter            & Mean value & Inter-quartile interval \\[0.5ex]
        \hline\hline
        $\lambda_N$          & 13.5       & [12.9, 14.2]            \\
        $a$                  & 0.0175     & [0.0145, 0.0207]        \\
        $\kappa_{N\beta}$    & 0.176      & [0.109, 0.234]          \\
        $\mu_N$              & 0.0239     & [0.0113, 0.0332]        \\
        $\nu_{N\Phi}$        & 0.125      & [0.115, 0.134]          \\
        \hline
        $\kappa_{\Phi\beta}$ & 0.123      & [0.115, 0.131]          \\
        $\mu_\Phi$           & 0.0234     & [0.0199, 0.0267]        \\
        \hline
        $s_{\beta N}$        & 2.38       & [2.02, 2.73]            \\
        $\mu_\beta$          & 2.67       & [2.24, 3.10]            \\
        \hline
        $s_{\alpha\Phi}$     & 0.574      & [0.295, 0.786]          \\
        $\mu_\alpha$         & 8.91       & [6.07, 11.1]            \\
        $f_{\beta\alpha}$    & 0.577      & [0.361, 0.738]          \\
        \hline
    \end{tabular}
    \caption[Estimated parameter values of model 3]
    {Estimated parameter values of model 3, using uniform prior distribution and log-uniform prior distribution respectively}
    \label{table:estimated5}
\end{table}

@@

@@

A quick sensitivity analysis of the dynamical systems models can be quantified using principle component analysis (PCA) \cite{Toni}, where the first PCs corresponds to sloppy parameters while the last PCs corresponds to stiff parameters \cite{sensitivity}. PCA can only provide rough approximated sensitivity behaviour. As models 5 won in the model selection, a further interest is to explore the parameter-to-model sensitivity

FIGURE shows the results of PCA on the last population of inferred model5. The last PC (PC12) is mostly consists of the linear combination of $a$ (from the equation of neutrophil) and $\mu_\Phi$ (from the equation of macrophage), to which the model is most sensitive. If we conclude the last 5 PCs (FIGURE), then $v_{N\Phi}$, $\mu_N)$ (from the equation of neutrophil) and $k_{\Phi\beta}$ (from the equation of macrophage) contribute most portions together with $a$ and $\mu_\Phi$. As a conclusion, model 5 is sensitive to changes in the above parameters, which all come from the equation of neutrophil and macrophage i.e. equations of the cells; it may suggests that given the observed data, the inferred model is more sensitive to cells' dynamic rather than cytokines' dynamics.

>>>>

\begin{table}[t!]
    \centering
    \begin{tabular}{|c c c|}
        \hline
        Parameter            & Mean value & Inter-quartile interval \\[0.5ex]
        \hline\hline
        $\lambda_N$          & 13.5       & [12.9, 14.2]            \\
        $a$                  & 0.0175     & [0.0145, 0.0207]        \\
        $\kappa_{N\beta}$    & 0.176      & [0.109, 0.234]          \\
        $\mu_N$              & 0.0239     & [0.0113, 0.0332]        \\
        $\nu_{N\Phi}$        & 0.125      & [0.115, 0.134]          \\
        \hline
        $\kappa_{\Phi\beta}$ & 0.123      & [0.115, 0.131]          \\
        $\mu_\Phi$           & 0.0234     & [0.0199, 0.0267]        \\
        \hline
        $s_{\beta N}$        & 2.38       & [2.02, 2.73]            \\
        $\mu_\beta$          & 2.67       & [2.24, 3.10]            \\
        \hline
        $s_{\alpha\Phi}$     & 0.574      & [0.295, 0.786]          \\
        $\mu_\alpha$         & 8.91       & [6.07, 11.1]            \\
        $f_{\beta\alpha}$    & 0.577      & [0.361, 0.738]          \\
        \hline
    \end{tabular}
    \caption[Inferred parameter values of model 5]
    {Inferred parameter values of model 5. MORE DETAIL(SUPER maxt-5)}
    \label{table:estimated5}
\end{table}

@@

\begin{figure}[h]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/overfit.png}}
    \end{center}

    \caption[Simulated trajectory from the last population of model 5, with factors applied]{Simulated trajectory from the last population of model 5, with factors applied. MORE DETAIL}
    \label{fig:overfit}
\end{figure}

@@

A quick sensitivity analysis of the dynamical systems models can be quantified using principle component analysis (PCA) \cite{Toni}, where the first PCs corresponds to sloppy parameters while the last PCs corresponds to stiff parameters \cite{sensitivity}. PCA can only provide rough approximated sensitivity behaviour. As models 5 won in the model selection, a further interest is to explore the parameter-to-model sensitivity.

\begin{figure}[t]
    \begin{center}
        \resizebox{0.8\hsize}{!}{\includegraphics{fig/pc_pie_all.png}}
    \end{center}

    \caption[TODO]{PCA results of the last population of model 5. MORE DESCRIPTION}
    \label{fig:pc}
\end{figure}

\begin{figure}[h]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/pc.png}}
    \end{center}

    \caption[PCA results of the last population of model 5]{PCA results of the last population of model 5. MORE DESCRIPTION}
    \label{fig:pc}
\end{figure}

FIGURE shows the results of PCA on the last population of inferred model 5. The last PC (PC12) is mostly consists of the linear combination of $a$ (from the equation of neutrophil) and $\mu_\Phi$ (from the equation of macrophage), to which the model is most sensitive. If we conclude the last 5 PCs (FIGURE), then $v_{N\Phi}$, $\mu_N)$ (from the equation of neutrophil) and $k_{\Phi\beta}$ (from the equation of macrophage) contribute most portions together with $a$ and $\mu_\Phi$. As a conclusion, model 5 is sensitive to changes in the above parameters, which all come from the equation of neutrophil and macrophage i.e. equations of the cells; it may suggests that given the observed data, the inferred model is more sensitive to cells' dynamic rather than cytokines' dynamics.
